---
title       : Lottery Presentation
subtitle    : present code
author      : tdpetrou
job         : Data Science Specialist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Playing the lottery

Have you ever wanted to generate random lottery numbers?

I know I have, but there isn't an easy way to do this on my android phone.

---

There are two different variables that you need in order to generate lottery numbers.

1. The total number of balls to be drawn from.
2. The number of balls to be drawn from that total

---

To do this we need the sample command in R, which when given two variables can produce the desired result.

Here is a function that accomplishes this for us.

```{r}
balls = 50
draws = 6
sample(1:balls, draws)
```

Now, its your turn. Guess 8 numbers between 1 and 100 before you go to the next slide and see if you win the lottery!

---

```{r}
balls = 100
draws = 8
sample(1:balls, draws)
```

## Did you win?

Message me on github for your prize!!

